---
title: "Wk5"
author: "Sookja Kang"
date: "9/23/2020"
output: html_document
---

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
```{r}
install.packages("tidytuesdayR")
install.packages("ggthemes")
install.packages("gganimate")
install.packages("gifski")
library(tidytuesdayR)
library(tidyverse)
library(ggthemes)
library(gganimate)
library(gifski)
```


```{r}
tuesdata <- tidytuesdayR::tt_load('2020-09-15')
#downloading the week data```
```


```{r}
tuesdata
```


```{r}
kids_data <- tuesdata$kids
view(kids_data)
```


```{r}
table(kids_data$variable)
str(kids_data)
```


```{r}
highered <- subset(kids_data, variable == "highered" & state == "Texas")
# or highered_data <- subset(kids_data, variable == "highered")
# texas_data <- subset(highered_data, state == "texas")
```

#ggplot(data, aes(x, y))

```{r}
ggplot(highered, aes(x = year, y = inf_adj_perchild)) + 
  geom_line() + 
  geom_point() +
  geom_smooth() +
  labs(title = "My First ggplot", 
       subtitle = "by Sookja Kang & Nathan Davis",
       x = "Year", y = "$ per child, inflation adjustment",
       caption = "source:tidykids") +
  theme_minimal() + 
  theme_bw() 

#If I do multiple themes, it only takes the last one. 
#empty () brings from the universial (global) aes in the first ().

 
```


```{r}
plot + theme_classic()

#how to do a line plot or histogram in R with GGplot2
#tutorials ggplots 2 any type
```


```{r}
plot + theme_minimal()
```


```{r}
plot + theme_economist()
```

```{r}
plot + theme_excel()
```

```{r}
texas_adj_data <- subset(kids_data, variable == "highered") %>%
  subset(grepl("Texas|Oklahoma|Arkansas|New Mexico|Louisiana", state))
```


```{r}
ggplot(texas_adj_data, aes(x = year, y = inf_adj_perchild)) +
  geom_point()+
  geom_line(aes(color = state)) + 
  labs(title = "Spending on higher Education, Texas and Bordering States",
       x = "Year", y = "$ per child (Adjusted for inflation)", 
       caption = "Source: tidykids")

```


```{r}
ggplot(texas_adj_data, aes(x = year, y = inf_adj_perchild)) +
  geom_point(aes(color = state))+
  geom_line(aes(color = state)) + 
  labs(title = "Spending on higher Education, Texas and Bordering States",
       x = "Year", y = "$ per child (Adjusted for inflation)", 
       caption = "Source: tidykids")
```


```{r}
ggplot(texas_adj_data, aes(x = year, y = inf_adj_perchild)) +
  geom_point(aes(color = state))+
  geom_line(aes(color = state), size = 2) + 
  labs(title = "Spending on higher Education, Texas and Bordering States",
       x = "Year", y = "$ per child (Adjusted for inflation)", 
       caption = "Source: tidykids")

```


```{r}
ggplot(texas_adj_data, aes(x = year, y = inf_adj_perchild, linetype = state)) +
  geom_point()+
  geom_line(size = 1) + 
  labs(title = "Spending on higher Education, Texas",
       x = "Year", y = "$ per child (Adjusted for inflation)", 
       caption = "Source: tidykids")
```


```{r}
ggplot(texas_adj_data, aes(x = year, y = inf_adj_perchild)) +
  geom_point(aes(color = state))+
  geom_line(aes(color = state), size = 2, linetype = "dotted") + 
  labs(title = "Spending on higher Education, Texas and Bordering States",
       x = "Year", y = "$ per child (Adjusted for inflation)", 
       caption = "Source: tidykids")
```
```{r}
facet_plot <- ggplot(texas_adj_data, aes(x = year, y = inf_adj_perchild)) +
  geom_point() +
  geom_line(size = 1)

facet_plot + facet_grid(rows = vars(state))
```


```{r}
facet_plot + facet_grid(cols = vars(state))
```

```{r}
ggplot(data = texas_adj_data, aes(x = year, y = inf_adj_perchild, color = state)) + 
  geom_bar(stat = "identity") + 
  labs(title = "Spending on Higher Education, Texas", 
       x = "Year", y = "$ perchild (Adjsted for Inflation)", 
       caption = "Source: tidykids")
```
```{r}
barchart <- ggplot(data = texas_adj_data, aes(x = year, y = inf_adj_perchild, fill = state)) + 
  geom_bar(stat = "identity") + 
  labs(title = "Spending on Higher Education, Texas", 
       subtitle = "by Sookja Kang",
       x = "Year", y = "$ perchild (Adjsted for Inflation)", 
       caption = "Source: tidykids")
barchart
```
```{r}
barchart + coord_flip()
```
```{r}
ggplot(data = texas_adj_data, aes(x = year, y= inf_adj_perchild, fill = state)) +
  geom_bar(stat="identity", position=position_dodge()) + 
  labs(title = "Spending on Higher Education, Texas", 
       subtitle = "by Sookja Kang",
       x = "Year", y = "$ perchild (Adjsted for Inflation)", 
       caption = "Source: tidykids")
```
```{r}
texas_adj_plot <- ggplot(texas_adj_data, aes(x = year, y = inf_adj_perchild)) +
  geom_line(aes(color = state), size = 2) +
  labs(title = "Spending on Higher Education, Texas and Bordering States, Year: {round(frame_along, 0)}",
       subtitle = "Source: tidykids",
       x = "Year", y = "$ per child (Adjusted for Inflation)",
       caption = "Josephine Lukito (for J381M|TidyTuesday)") +
    transition_reveal(year) +
  theme_minimal() + #use the theme_minimal default
  theme(plot.title = element_text(size = 24, face = "bold"), #change the plot f
        plot.subtitle = element_text(size = 18),
        axis.title = element_text(size = 18), axis.text = element_text(size = 16),
        legend.position = "bottom", #moves the legend to the bottom
        legend.title = element_text(size = 16, face = "bold"), 
        legend.text = element_text(size = 16)
  )
animate(texas_adj_plot, height = 700, width = 1000) #you will see the plot in viewer()
viewer()
```


```{r}
```


```{r}
) 
```{r}